SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-09-20 scipy-1.0/paper.tex
Add notes on introduction; transition into conferences section, expand.

\fixme{The Introduction section expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.}

@@

In 2000, STScI ported their entire IDL-based analysis pipeline, IRAF,
to Python.  And it was here that a small crisis developed around the
Python numerical array container.  Numeric, the original array package, was
suitable for small arrays, but not for the large images processed by
STScI.  With the Numeric maintainer's blessing, the decision was made
to write NumArray, a library that could handle data on a different
scale.  Unfortunately, NumArray proved inefficient for small arrays,
presenting the community with a rather unfortunate choice.  In 2005,
Travis Oliphant combined the best elements of Numeric and NumArray,
thereby solving the dilemma and paving the way for Python to become
a very significant player in the Data Science movement. \fixme{mention
  first NumPy meeting at Berkeley}

@@

@@

SciPy

US, India, Europe

@@

\cite{dubois2007guest}
\cite{oliphant2007python}
\cite{perez2007ipython}
\cite{hunter2007matplotlib}
\cite{vanderwalt2008scipy}
\cite{peterson2009f2py}
\cite{millman2011python}
\cite{perez2011python}
\cite{vanderwalt2011numpy}
\cite{behnel2011cython}
\cite{pedregosa2011scikit}
\cite{vanderwalt2014scikit}
\cite{millman2014developing}
\cite{meurer2017sympy}

>>>>

\begin{verbatim}
SciPy is not what you think it is

- At risk of failure many times
- Funding was *hard* to come by; funding agencies didn't easily give
  money.  Some labs, Enthough committed a bit of money.
- Java and other enterprize packages were getting support; MATLAB
  was huge.  Not many wanted to encourage this ``amateur'' effort.
- Graduate students & post-docs doing the heavy lifting; they found
  a system they enjoyed using, saw its potential, put energy into it.
- Driven by eclectic group of people being passionate about it, not
  because they were paid or told to work on it.
- And not by EECS people, but by scientists.  Some with fairly little
  programming background (David), others in varying stages of academic/research careers.
- Over time, the project became more more professional:
  - Standardized release formats
  - Docstrings
  - Testing & CI infrastructure
  - APIs
  - Issue tracking
  - Revision control (CVS -> SVN -> Git)
  - Conference
- Python wasn't perfectly suited in all ways; packaging, compiling,
  indexing (indexing/array protocols and complex numbers added)
- Initially, this high quality, stable, widely used project, hinged on
  three people doing the ``right'' thing to get it established.
- Bus factor for maintenance still very low.

The background section captures a selective history where we're trying
to identify some of the more important events.  But really, it relies
on the collective work of numerous individuals, too many to mention.
\end{verbatim}

@@

In 2000, STScI ported their entire IDL-based analysis pipeline, IRAF,
to Python.  And it was here that a small crisis developed around the
Python numerical array container.  Numeric, the original array package, was
suitable for small arrays, but not for the large images processed by
STScI.  With the Numeric maintainer's blessing, the decision was made
to write NumArray, a library that could handle data on a different
scale.  Unfortunately, NumArray proved inefficient for small arrays,
presenting the community with a rather unfortunate choice.  In 2005,
Travis Oliphant combined the best elements of Numeric and NumArray,
thereby solving the dilemma and paving the way for Python to become
a very significant player in the Data Science movement.

@@

SciPy now begins a phase of significant growth and adoption.  The
informal workshops are grown into international conferences with many
hundreds of attendees, special issues are organized and published in a
leading scientific magazine, and the scope of the SciPy library
narrows, while the breadth of the ecosystem is grown and encouraged
through a new type of auxhilary package, the scikit.  The tooling,
development and release processes become more professional, grown with
a patience only affordable in open source development, leading with
best practices nowadays increasingly common in both industry and other
open source projects \cite{millman2014developing}.

@@

In 2008, the SciPy conference went from being a small gathering of
core developers, to a multi-location event, with increased funding, a
published proceedings, and scholarships for attending students (some
of whom are authors on this paper).  In 2010, the conference grew even
further, with an additional event added in India, and the US
conference—now with parallel tracks—moving to Austin, Texas.

@@

\cite{dubois2007guest}
\cite{oliphant2007python}
\cite{perez2007ipython}
\cite{hunter2007matplotlib}
\cite{vanderwalt2008scipy}
\cite{peterson2009f2py}
\cite{millman2011python}
\cite{perez2011python}
\cite{vanderwalt2011numpy}
\cite{behnel2011cython}
\cite{pedregosa2011scikit}
\cite{vanderwalt2014scikit}
\cite{meurer2017sympy}
